pema application

### 2022-12-01 paper/manuscript.Rmd
final corrections ammend; iterations

Before interpreting the results, however,
it is important to assess model convergence.
If any indication of non-convergence is detected during estimation,
a warning will be printed.
The example returns the warning that there were 331 divergent transitions,
and suggests increasing the number of iterctions (increasing the argument `iter` beyond its default value of 2000).
Divergent transitions can result in biased estimates.
If the number of divergences is small and there are no further indications of non-convergence, however,
the posterior distribution is often good enough to safely interpret the results.
We can examine two parameter-specific indicators of convergence
by ascertaining that the number of "unique" samples from the posterior `n_eff` for each parameter is sufficiently high,
and that the different chains of the estimator have mixed properly, as indicated by `Rhat` close to 1.
The number of effective (independent) MCMC samples should be high relative to the total number of samples (in this case, 4000, as we used 2000 iterations on a dual-core processor).
If the effective sample size is less than 10% of the total,
there may be a problem - which is not the case here.
The `Rhat` is a version of the potential scale reduction factor,
which represents the ratio of between- and within-chain variance [@GelmanRubin1992].
If the chains mixed well, the `Rhat` should be close to 1.
Both `n_eff` and `Rhat` indicate convergence in this example.
Additional convergence diagnostics are obtained by running `check_hmc_diagnostics(as.stan(fit))`.
Convergence can also be assessed visually using the function `traceplot(as.stan(fit), pars = c("Intercept", "year"))`,
which provides trace plots for the MCMC draws.
If the model converged, the traces of the different chains should mix well (i.e., overlap) and look like "fat caterpillars".

>>>>

Before interpreting the results, however,
it is important to assess model convergence.
If any indication of non-convergence is detected during estimation,
a warning will be printed.
The example returns the warning that there were 331 divergent transitions,
and suggests increasing the number of iterations (increasing the argument `iter` beyond its default value of 2000).
Divergent transitions can result in biased estimates.
If the number of divergences is small and there are no further indications of non-convergence, however,
the posterior distribution is often good enough to safely interpret the results.
We can examine two parameter-specific indicators of convergence
by ascertaining that the number of "unique" samples from the posterior `n_eff` for each parameter is sufficiently high,
and that the different chains of the estimator have mixed properly, as indicated by `Rhat` close to 1.
The number of effective (independent) MCMC samples should be high relative to the total number of samples (in this case, 4000, as we used 2000 iterations on a dual-core processor).
If the effective sample size is less than 10% of the total,
there may be a problem - which is not the case here.
The `Rhat` is a version of the potential scale reduction factor,
which represents the ratio of between- and within-chain variance [@GelmanRubin1992].
If the chains mixed well, the `Rhat` should be close to 1.
Both `n_eff` and `Rhat` indicate convergence in this example.
Additional convergence diagnostics are obtained by running `check_hmc_diagnostics(as.stan(fit))`.
Convergence can also be assessed visually using the function `traceplot(as.stan(fit), pars = c("Intercept", "year"))`,
which provides trace plots for the MCMC draws.
If the model converged, the traces of the different chains should mix well (i.e., overlap) and look like "fat caterpillars".
